Submission and Formatting Instructions for \\ International Conference on Machine Learning (ICML 2019)

### 2019-04-24 paper/icml_ai4good/main.tex
intro is finished, adding references now

Recent work by \citep{Baydin} introduces a fundamental paradigm change that, for the first time, allows to tackle this inverse problem in a way that .

@@

In this paper, we for the first time demonstrate the applicability of trace introspection, and hence universal probabilistic inference, to population-based simulators. In particular, we discuss how the leading malaria epidemiology simulators EMOD[] and OpenMalaria[] can be interfaced with <TODO>. We argue that our work is likely to have significant social impact on many livelihoods affected by Malaria and discuss opportunities for future research.

- issues of public health are complex and

>>>>

Recent work by \citep{Baydin} introduces a fundamental paradigm change that allows to tackle the inverse problem directly. Using a novel software tool named \textit{pyprob}, \citep{Baydin} extract program execution traces from state-of-the-art particle decay simulation engine SHERPA\cite{}. Using latest techniques from universal probabilistic programming inference, the sampled execution traces are then used in order to characterise the posterior distribution of the simulator output. From these, regions in simulator input space can be associated with specified outcomes.

SHERPA, however, is different from leading epidemiology simulators in that it does not simulate population dynamics, but instead models individual decays at a time. In this paper, we for the first time demonstrate the applicability of \textit{pyprob}, and hence probabilistic programming inference, to population-based epidemiology simulators. In particular, we discuss how the leading malaria epidemiology simulators EMOD\cite{} and OpenMalaria\cite{} can be interfaced with \textit{pyprob}. We argue that our work is likely to have significant social impact on many livelihoods affected by Malaria and discuss opportunities for future research.

@@

%- issues of public health are complex and
